Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

Consider two  pairs that share the same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a~non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost to \OPT only the first time \RM collocates a~pair,
and not at any consequent time when \RM collocates it a~second time.
Otherwise,
 \OPT is possibly charged for the same cost repeatedly.
For this reason,
we charge \OPT a~cost inflicted by a~pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%

>>>>

Consider two  pairs that share the same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a~non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost \maciek{Whole cost unclear, I think} to \OPT only the first time \RM collocates a~pair,
and not at any consequent time when \RM collocates it a~second time.
Otherwise,
 \OPT is possibly charged for the same cost repeatedly.
For this reason,
we charge \OPT a~cost inflicted by a~pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%
